A systematic search for transiting planets in the \KT\ data

### 2015-02-13 ms.tex
outline and injections

The \paper\ is organized as follows.
In \textsection\ref{sec:phot}, we describe our analysis of the photometric
data collected by \KT.
In \textsection\ref{sec:model}, we expain our simultaneous fit of the
systematics and transit model.
In \textsection\ref{sec:search}, we describe our search pipeline for
planet candidates.
In \textsection\ref{sec:perform}, we quantify the performace of our pipeline
through the analysis of injected planetary signals.
In \textsection\ref{sec:K2OIs}, we present the results of our search:
catalogs of \KT\ planet candidates and eclipsing binaries.
In \textsection\ref{sec:discuss}, we discuss our results and outline our
future work.

\section{Photometry}
\label{sec:phot}

@@

\section{Search pipeline}
\label{sec:search}

@@

In \KT, the precision of these tests is lower and they must be applied with
care.
There are typically only a handful of transits, meaning differences between
``odd'' and ``even'' transits must be large to create a significant
difference.
Searching for ellipsoidal varaitions is hindered by the short time baseline
and the increased photometric uncertainty in \KT\ data.
Centroid variations are feasible in \KT\ but must be treated differently than
in the original \kepler\ mission where this effect was generally measured
using difference imaging (cite Howell).

To obtain an initial assessment of the astrophysical false positive rate in
our catalog of planet candidates, we test for centroid offsets and variable
depth transits using the machinery that we have already established for
modeling the systematic trends in the data.
This is only the first word and a more complete characterization of our
catalog's reliability is forthcoming (Montet, Foreman-Mackey, \etal\ in prep).

To measure \emph{centroid offsets}, we start by empirically measuring the
pixel centroid time series for each candidate by modeling the pixels near the
peak as a two-dimensional quadratic and finding the maximum at each time.
This method has been shown to produce higher precision centroid measurements
than center-of-light estimates (@HOGG: is this true? Is there a citation? MJ
in prep?).
Figure SOMEFIGURE shows the measure $x$ and $y$ pixel coordinate traces for
SOMECANDIDATE.
Much like the photometry, this signal is dominated by the rigid body motion
of the spacecraft and we can, in fact, model it identically.
Previously (SOMEEQUATION), we modeled the light curve as a linear combination
of ELCs and a simple box transit model at a given period, phase, and duration.
Under this model, the maximum likelihood depth can be computed analytically.
If we apply \emph{exactly the same model} to the centroid trace, the ``depth''
that we compute becomes the centroid motion in transit in units of pixels.
Since the motions won't necessarily point in a consistent direction across
transits, we treat each transit independently and report the average offset
amplitude weighted by the precision of each measurement.
To compute the significance of a centroid offset, we bootstrap the offset
amplitude for models at the same period and duration but randomly oriented
phases.
If the centroid measured for the candidate transit is substantially larger
(by SOMEAMOUNT) than the random realizations, then the candidate is labeled
as a false positive.
Figure SOMEFIGURE shows the distribution of centroid offsets across our
catalog and YYYY---or ZZZZ\%---of our candidates fail this test.

We also test the consistency \emph{between even and odd transit depths} for
each of our candidates.
As described in SOMESECTION, our method for transit search automatically
rejects signals with wildly varying depths but.

Blah blah blah.
Therefore, false positives caused by background eclipsing binaries which could
be identified as such by \kepler\ data alone will be much more difficult to
distinguish in \KT\ data, making high-contrast adaptive optics images of
planet candidates an essential follow-up tool.

\section{Performance}

To test the performance of our method, we conducted a suite of XXXX injection
and recovery tests.
For each test, we inject the signal from a realistic planetary system into the
raw aperture photometry and passed it through the full pipeline.
These synthetic systems have periods and radius ratios drawn uniformly in
\dfmtodo{some range} and uniformly distributed impact parameters and phases.
The eccentricities are drawn from a beta distribution with \dfmtodo{some
parameters; cite Kipping} and the multiplicity is set to match the observed
multiplicity distribution in the KOI catalog \dfmtodo{cite}.
MA limb darkening, exposure time integration, etc.

@@

\section{Results}

@@

\section{Mathematical model}\sectlabel{math}

>>>>

The \paper\ is organized as follows.
In \sect{phot}, we describe our method of extracting aperture photometry from
the calibrated \KT\ postage stamp time series.
In \sect{model} (with details in \app{math}), we describe our data-driven
model for the systematic trends in the photometric light curves and our method
for fitting this model simultaneously with a transit signal.
In \sect{search}, we give the detailed procedure that we use for discovering
and vetting planet candidates.
To quantify the performance and detection efficiency of our pipeline, we test
(in \sect{perform}) the recovery and false alarm rate of synthetic transit
signals, spanning a large range of physical parameters, injected into real
\KT\ light curves.
Finally, in \sect{results}, we present a catalog of XXXX planet candidates
orbiting WWWW stars---and a supplementary list of YYYY eclipsing binary
candidates---in the publicly available \KT\ Campaign 1 dataset.

\section{Photometry}
\sectlabel{phot}

@@

\section{Search pipeline}
\sectlabel{search}

@@

In \KT, the precision of these tests is lower and they must be applied with
care.
There are typically only a handful of transits, meaning differences between
``odd'' and ``even'' transits must be large to create a significant
difference.
Searching for ellipsoidal variations is hindered by the short time baseline
and the increased photometric uncertainty in \KT\ data.
Centroid variations are feasible in \KT\ but must be treated differently than
in the original \kepler\ mission where this effect was generally measured
using difference imaging (cite Howell).

To obtain an initial assessment of the astrophysical false positive rate in
our catalog of planet candidates, we test for significant centroid offsets
using the machinery that we have already established for modeling the
systematic trends in the data.
This is only the first word and a more complete characterization of our
catalog's reliability is forthcoming (Montet, Foreman-Mackey, \etal\ in prep).

To measure \emph{centroid offsets}, we start by empirically measuring the
pixel centroid time series for each candidate by modeling the pixels near the
peak as a two-dimensional quadratic and finding the maximum at each time.
This method has been shown to produce higher precision centroid measurements
than center-of-light estimates (@HOGG: is this true? Is there a citation? MJ
in prep?).
Figure SOMEFIGURE shows the measure $x$ and $y$ pixel coordinate traces for
SOMECANDIDATE.
Much like the photometry, this signal is dominated by the rigid body motion
of the spacecraft and we can, in fact, model it identically.
Previously (\eqalt{linear-model}), we modeled the light curve as a linear
combination of ELCs and a simple box transit model at a given period, phase,
and duration.
Under this model, the maximum likelihood depth can be computed analytically.
If we apply \emph{exactly the same model} to the centroid trace, the ``depth''
that we compute becomes the centroid motion in transit in units of pixels.
Since the motions won't necessarily point in a consistent direction across
transits, we treat each transit independently and report the average offset
amplitude weighted by the precision of each measurement.
To compute the significance of a centroid offset, we bootstrap the offset
amplitude for models at the same period and duration but randomly oriented
phases.
If the centroid measured for the candidate transit is substantially larger
than the random realizations, we label the candidate as a false positive.
In practice, the precision of the centroid measurements isn't sufficient to
robustly reject many candidates but of the list of 100 (RIGHT NUMBER), two
candidates---EPIC AAA and BBB---have offsets large enough that we remove them
from our final catalog.
Figure SOMEFIGURE shows the distribution of centroid offsets across the full
catalog.

\section{Performance}
\sectlabel{perform}

To test the performance and detection efficiency of our method, we conducted a
suite of XXXX injection and recovery tests, this is the result of 5 tests per
star.
For each test, we inject the signal from a realistic planetary system into the
raw aperture photometry of a random target and run the resulting light curve
through the full pipeline.
If the search returns a planet candidate---passing all of the same cuts as we
apply in the main search---with period and reference transit time within
HOWMANY days of the injected signal, we count that injection as recovered.
The detection efficiency of the search is approximately given by the fraction
of recovered injections as a function of the relevant parameters.

These synthetic systems have periods and radius ratios drawn uniformly in
\dfmtodo{some range} and uniformly distributed impact parameters and phases.
The eccentricities are drawn from a beta distribution with \dfmtodo{some
parameters; cite Kipping} and the multiplicity is set to match the observed
multiplicity distribution in the KOI catalog \dfmtodo{cite}.
MA limb darkening, exposure time integration, etc.

@@

\section{Results}
\sectlabel{results}

@@

\section{Mathematical model}
\sectlabel{math}
